Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-22 cav2017/cav2017.tex
one comment

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilizing controllers for continuous plants
by exploiting advantage in bit-accurate verification of C programs 
to obtain a verifier for software-implemented digital control~\cite{Bessa16}.  
While they also make use of a CEGIS-based technique, their approach is
restricted to synthesising controllers for hybrid closed-loop systems
that are stable and only consider transfer function models.  In contrast,
in the current paper, we consider a state-space
representation of the physical system and synthesise controllers that
make the closed-loop system safe.  Moreover, 
a key aspect of our approach
is the fact that we integrate abstraction
refinement inside the CEGIS loop.

We require a combination of a synthesis engine with a control
verification tool that addresses the challenges presented here in the
form of FWL effects and stability measures for LTI SISO controllers.
We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
from~\cite{daes20161}, while enhancing the procedure by evaluating the
quantization effects of the Hardware interfaces (ADC/DAC) to obtain an
accurate discrete-time FWL representation of the continuous dynamics.

>>>>

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilizing controllers for continuous plants
by exploiting advantage in bit-accurate verification of C programs 
to obtain a verifier for software-implemented digital control~\cite{Bessa16}.  
While they also make use of a CEGIS-based technique, their approach is
restricted to synthesising controllers for hybrid closed-loop systems
that are stable and only consider transfer function models.  In contrast,
in the current paper, we consider a state-space
representation of the physical system, which allows us to synthesise controllers that
make the closed-loop system \emph{safe} as well as stable.  Moreover, 
a key aspect of the second approach we evaluate
is the fact that we integrate abstraction
refinement inside the CEGIS loop.

We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented here in the
form of FWL effects and stability measures for LTI SISO controllers.
We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
from~\cite{daes20161}\todo{This paper seems to be for transfer functions, not state space,
is there a paper that does state space stability and safety?}
, while enhancing the procedure by evaluating the
quantization effects of the Hardware interfaces (ADC/DAC) to obtain an
accurate discrete-time FWL representation of the continuous dynamics.
